% MUST be compiled using the --shell-escape tag. "pdflatex --shell-escape main.tex"

\documentclass{article}
\input{Preamble.tex}
\usepackage[utf8]{inputenc}
\usepackage{gnuplottex}
\usepackage{tkz-fct}
\usepackage{graphicx}
\graphicspath{ {./images/} }

\title{The Application and Investigation of Lissajous Curves}
\author{Alyssa Eckerman, Elias Little}
\date{May 2019}

\pgfplotsset{compat=1.13}
\begin{document}

\maketitle
\section{History}
\input{Parts/History.tex}
\newpage
\section{Mathematical Components}
\input{Parts/MathComponents.tex}
\newpage
\section{Arc Length}
\input{Parts/ArcLength.tex}
\newpage
\section{Path Integral}
\input{Parts/PathIntegrals.tex}
\newpage
\section{Contributions}
\input{Parts/Contributions.tex}
\section{Conclusion}
\input{Parts/Conclusion.tex}
\newpage
\begin{thebibliography}{9}
%\bibitem{latexcompanion}
%Michel Goossens, Frank Mittelbach, and Alexander Samarin.
%\textit{The \LaTeX\ Companion}.
%Addison-Wesley, Reading, Massachusetts, 1993.
\bibitem{Harmonograph}
“Beautiful Curves: The Harmonograph.” \textit{Fronkonstin}, 26 Sept. 2016, \texttt{fronkonstin.com/2014/10/13/beautiful-curves-the-harmonograph/}

\bibitem{LissajousFigures}
Greenslade, Thomas  B. “Lissajous Figures.” \textit{Instruments for Natural Philosophy}, \texttt{physics.kenyon.edu/EarlyApparatus/Oscillations\_and\_Waves/Lissajous\_Figures/
Lissajous\_Figures.html.}

\bibitem{JulesAntoineLissajous}
“Jules Antoine Lissajous (1822--1880) --- Historical Sketch.” \textit{Hardy Calculus,}
\texttt{hardycalculus.com/calcindex/IE\_lissajous.htm.}

\bibitem{PhaseShift}
Krishnavedala. "Figure showing several Lissajous figures for different phase delays."
\textit{Wikipedia}, Wikipedia, 20 Aug. 2014, \texttt{https://en.wikipedia.org/wiki/Lissajous\_curve\#/media/File:Lissajous\_phase.svg}

\bibitem{Onlinecurve}
“Lissajous Curves.” \textit{Lissajous Curves | Academo.org - Free, Interactive, Education.},\texttt{ academo.org/demos/lissajous-curves/}

\bibitem{Oscilloscope}
“Lissajous Figure.” \textit{Encyclopaedia Britannica}, 20 July 1998, \texttt{www.britannica.com/science/Lissajous-figure}

\bibitem{NathanielBowditch}
“Nathaniel Bowditch (1773--1838) --- Historical Sketch.” \textit{Hardy Calculus}, \texttt{hardycalculus.com/calcindex/IE\_bowditch.htm}

\bibitem{Harmpic}
Sims, Karl. “Harmonograph.” \textit{Karl Sims}, www.karlsims.com/harmonograph/

\bibitem{3DCurve}
Trott, Michael. “3D Lissajous Curve with Avoided Intersections.”\textit{Wolfram Demonstrations Project}, demonstrations.wolfram.com/

\end{thebibliography}
\end{document}
